OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-22 tex/description.tex
Order => ordering, practical fixed => practically fixed

%TODO mandatory: add short abstract of the document
\begin{abstract}
  Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization}
  (OCM) problem is to find an order of the vertices of $B$ that minimizes the
  number of edge crossings when drawn in the plane.

  We prove a number of novel reductions, and apply these in our solver OCMu64
  that directly uses branch-and-bound on the order of the vertices of $B$ and
  does not depend on ILP or SAT solvers.
\end{abstract}

@@

\begin{description}
  \item[Graph simplification] We drop degree-$0$ vertices, merge identical
    vertices, and split the graph into \emph{independent} components when
    possible. We find an initial solution using local search that tries to move
    slices and optimally insert them, and re-label all nodes accordingly to make
    memory accesses more efficient.
  \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
    exact track we also find practical fixed pairs. Instances for the parameterized
    track are simple enough that the overhead was not worth it. Also for each
    tail we search for new `tail-local' practical fixed pairs. In each state, we only
    try vertices $u\in T$ not fixed by another $v\in T$.
  \item[Gluing] We use the greedy strategy of \cref{greedy}. Our implementation
    of \cref{pg} contained a bug, so we did not use this. (Also benefits
    seemed limited.)
  \item[Tail cache] In each step, we search for the longest suffix of $T$ that
    was seen before, and reuse (the lower bound on) its excess. We also
    cache the tail-local practical fixed pairs.
  \item[Optimal insert] Instead of simply appending $u$ to $P$, we
    insert it in the optimal position. Note that the
    implementation is tricky because it interacts in complicated ways with
    the caching of results for each tail.
\end{description}
\end{document}

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
  Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization}
  (OCM) problem is to find an ordering of the vertices of $B$ that minimizes the
  number of edge crossings when drawn in the plane.

  We prove a number of novel reductions, and apply these in our solver OCMu64
  that directly uses branch-and-bound on the ordering of the vertices of $B$ and
  does not depend on ILP or SAT solvers.
\end{abstract}

@@

\begin{description}
  \item[Graph simplification] We drop degree-$0$ vertices, merge identical
    vertices, and split the graph into \emph{independent} components when
    possible. We find an initial solution using local search that tries to move
    slices and optimally insert them, and re-label all nodes accordingly to make
    memory accesses more efficient.
  \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
    exact track we also find practically fixed pairs. Instances for the parameterized
    track are simple enough that the overhead was not worth it. Also for each
    tail we search for new `tail-local' practically fixed pairs. In each state, we only
    try vertices $u\in T$ not fixed by another $v\in T$.
  \item[Gluing] We use the greedy strategy of \cref{greedy}. Our implementation
    of \cref{pg} contained a bug, so we did not use this. (Also benefits
    seemed limited.)
  \item[Tail cache] In each step, we search for the longest suffix of $T$ that
    was seen before, and reuse (the lower bound on) its excess. We also
    cache the tail-local practically fixed pairs.
  \item[Optimal insert] Instead of simply appending $u$ to $P$, we
    insert it in the optimal position. Note that the
    implementation is tricky because it interacts in complicated ways with
    the caching of results for each tail.
\end{description}
\end{document}
